---
title: "chatbot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{chatbot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(vktools)
library(httr2)
library(purrr)
```

set API keys
```{r keys}
openai_key <- Sys.getenv("OPENAI_API_KEY")
# openai_key <- Sys.getenv("OPENAI_TECH_KEY")
```

Get assistants available in OpenAI account
```{r get_assistans}
############################################### GET ASSISTANTS
assistants <- httr2::request('https://api.openai.com/v1/assistants') %>% req_openai(openai_key)
assistants$data[[1]]
```

List available models in openAI account
```{r get_models}
############################################### LIST AVAILABLE MODELS
models <- httr2::request('https://api.openai.com/v1/models') %>% req_openai(openai_key)
models$data %>% dplyr::bind_rows() %>% View()
```

Create an assistant with custom instructions
```{r create_assistant}
############################################### CREATE NEW ASSISTANT
new_assistant <- httr2::request('https://api.openai.com/v1/assistants') %>%
  req_body_json(
    data = list(
      model = 'gpt-4-0125-preview',
      name = 'Vikua Data Analyst',
      description = 'Assistant for Vikua Data Analysis tasks and use cases. First of his kind, treat it well, he is a pioneer.',
      instructions = 'You are a personal Data analyst. When asked a question, write and run Python code to answer concisely.
      Try to focus on business insights that the user cannot see without processing data. 
      If the user provide data, use it to generate insights and answer questions.
      when describing insights, start the text with "### Insights Generados"',
      tools = list(
        list(
          type = 'code_interpreter'
        ),
        list(
          type = 'retrieval'
        )
      )
    )
  ) %>% 
  req_openai(openai_key)

# assistant_id <- 'asst_BcxFXLk5xZAbdmKrC2YApZs5'
```

Get available files in OpenAI account
```{r get_files}
############################################### GET FILES
files <- request('https://api.openai.com/v1/files') %>% req_openai(openai_key, beta = FALSE, app_json = FALSE)
files$data
```

Upload a file. This is usefull to later pass the file ID to a thread an get insights of the dataset
```{r upload_files}
############################################### UPLOAD A FILE
file_uploaded <- upload_file_openai(
  prima_a_renovar,
  openai_key,
  'vikua/urban_intelligence/real_seguros/prima_a_renovar.csv')
```

Create a thread and run it
```{r create_thread}
############################################### CREATE THREAD
thread <- create_thread_openai(openai_key)
thread_id <- thread %>% pluck('id')

############################################### RUN THREAD
# thread_id <- 'thread_dJu1ZrgAppnlNMXy1lOluV9K'

# assistant_log <- readr::read_csv('vikua/urban_intelligence/real_seguros/assistant_log.csv')
# after_mssg <- assistant_log$id[[1]]
```

Send message to a thread
```{r send_message}
message <- send_message_openai(
  thread_id, 
  assistant_id, 
  "Genera dos insights interesantes sobre el archivo que te estoy enviando. La data proviene de una aseguradora.
  enfocate en el riesgo financiero o algun otro angulo que le sirva a una empresa aseguradora. El archivo es un csv, esta delimitado
  por comas y los decimales de los campos numericos se separan con punto", 
  openai_key, 
  file_uploaded$id
)

thread_messages <- run_thread_openai(thread_id, assistant_id, openai_key, before_mssg = message$id)
# thread_messages <- list_messages_openai(thread_id, openai_key)
```

Log the response of the assistant
```{r log_response}
############################################### LOG RESPONSE
log_response(thread_messages, file_uploaded$filename, 'vikua/urban_intelligence/real_seguros/assistant_log.csv')
```

Remove the file uploaded
```{r log_response}
############################################### REMOVE A FILE
remove_file_openai(file_uploaded$id)
# remove_file('file-5A5y97NtPhsNOQxLvbob5DsD')
```

Retrive file content to inspect if it uploads correctly
```{r retrieve_file_content}
############################################### RETRIEVE FILE CONTENT
# file_content <- retrieve_file_content_openai(file_uploaded$id, openai_key)
# file_content <- retrieve_file_content_openai('file-Fczc03lEeqqvPOnxhC0UX8YY', openai_key)
```

Modify instructions of an assistant
```{r modify_assistant_instruction}
############################################### MODIFY ASSISTANT INSTRUCTION
new_assistant <- request('https://api.openai.com/v1/assistants') %>%
  req_url_path_append(assistant_id) %>%
  req_body_json(
    data = list(
      instructions = 'You are a personal Data analyst. When asked a question, write and run Python code to answer concisely.
      Try to focus on business insights that the user cannot see without processing data. 
      If the user provide data, use it to generate insights and answer questions.
      When describing insights, start the text with "### Insights Generados"'
    )
  ) %>% 
  req_openai(openai_key)

```

